Analysis Report

### 2019-04-18 analysis/analysis_report.rmd
basic analysis report done

---
title: "Analysis_Report"
author: "Daniel Pearson"
date: "11 April 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(R.matlab)
library(afex)
library(emmeans)
library(here)
library(patchwork)
library(cowplot)
library(BayesFactor)
library(hrbrthemes)
library(ggsignif)

@@

# Behavioural Analysis

@@

```{r Remove participants with poor gaze data}
propCutoff <- .5
allTracks <- exptdata %>%
  group_by(sub) %>%
  summarise(fixationProp = mean(fixationPropGoodSamples),
            trialProp = mean(trialPropGoodSamples))

@@

We removed data for any participants who did not have sufficient quality gaze data. If participants have an average of less than `r propCutoff*100`% valid gaze data during the fixation period or during a trial, they are removed from the data set.

`r length(poortracks)` participants were removed due to having a poor track.

@@

#  check to make sure that everyone has completed the full 480 trials
didNotComplete <- exptdata %>%
  group_by(sub) %>%
  filter(block > 0) %>%
  tally() %>%
  filter(n < 480) %>%
  select(sub)

@@

`r length(remove_p_numbers)` participants were removed for other reasons (participant #37 they thought that they needed to look at the coloured circle in order to earn rewards, participant #26 and #85 did not complete the experiment due to difficulty tracking their eyes).

Then we remove the first two trials of the experiment, the first two trials after breaks, and timeouts from the data (in line with previous VMAC analysis protocols):

@@

## Omission Trials
```{r Omission Trial Means}
exptdata_means_byparticipant <- exptdata %>%
  ungroup() %>%
  group_by(sub, condition, dType) %>%
  summarise(m = mean(omissionTrial))

exptdata_means_bycondition <- summarySEwithin2(data = exptdata_means_byparticipant, measurevar = "m", betweenvars = "condition", withinvars = "dType", idvar = "sub") %>%
  select(-ends_with("Normed"))
```

```{r Omission Trial Graph}

omissionPlot_singleton <- exptdata %>%
  filter(condition == "Singleton Search") %>%
  group_by(sub, dType) %>%
  summarise(m = mean(omissionTrial)) %>%
  ggplot(aes(x = dType, y = m, fill = dType, shape = dType)) +
  geom_errorbar(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m, ymin = m-se, ymax = m+se), colour = "black", width = .15) +
  geom_line(aes(group = sub), colour = "black", alpha = .1, linetype = "solid", size = .5) +
  geom_line(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m, group = 1), colour = "black") + 
  geom_point(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m), colour = "black", size = 3) +
  geom_signif(comparisons = list(c("High", "Low"), c("Low", "Absent")), annotations = c("***","*"), y_position = c(.61,.57), colour = "black", tip_length = 0) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) +
  scale_x_discrete(labels = c("High\nreward", "Low\nreward", "Distractor\nabsent")) +
  scale_fill_manual(values = vmacCols) +
  scale_colour_manual(values = vmacCols) +
  scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22,23)) +
  labs(y = "% Reward Omissions", x = "Trial Type", tag = "A", title = "Singleton Search") +
  my_theme

@@

### Effect of Reward
Effect of reward ANOVA:
```{r Effect of Reward - Omissions}
omissions_vmac.ANOVA <- aov_car(m ~ condition*dType + Error(sub/dType), data = filter(exptdata_means_byparticipant, dType != "Absent"), anova_table = list(es="pes"))
```
Significant main effect of reward (indicating VMAC effect), but no interaction with or main effect of search condition.

Planned t-tests:
```{r Effect of Reward - Omissions - Planned t-tests}
singleton_high_omissions <- exptdata_means_byparticipant %>%
  ungroup() %>%
  filter(condition == "Singleton Search") %>%
  filter(dType == "High") %>%
  select(m) %>%
  pull()

@@

singleton_VMAC_omissions.ttest <- t.test(singleton_high_omissions, singleton_low_omissions, paired = T)
singleton_VMAC_omissions.es <- dz_calculator(singleton_high_omissions, singleton_low_omissions)
feature_VMAC_omissions.ttest <- t.test(feature_high_omissions, feature_low_omissions, paired = T)
feature_VMAC_omissions.es <- dz_calculator(feature_high_omissions, feature_low_omissions)

@@

vmac_condition_bayes <- ttestBF(x = vmac_singleton, y = vmac_feature)
```

@@

omissions_salience.ANOVA
```

Planned t-tests:
```{r Effect of Physical Salience - Omissions - Planned t-tests}
singleton_physicalsalience_omissions.ttest <- t.test(singleton_low_omissions, singleton_absent_omissions, paired = T)

singleton_physicalsalience_omissions.es <- dz_calculator(singleton_low_omissions, singleton_absent_omissions)

feature_physicalsalience_omissions.ttest <- t.test(feature_absent_omissions, feature_low_omissions, paired = T) # reverse the order here so can get positive t value

feature_physicalsalience_omissions.es <- dz_calculator(feature_low_omissions, feature_absent_omissions)
```

@@

## First saccade direction
```{r First saccade direction - means}
# calculate summary statistics for each participant
saccadeData_means_byparticipant <- saccadedata %>%
  ungroup() %>%
  mutate(sub = as.factor(sub)) %>%
  group_by(sub, condition, dType) %>%
  summarise(saccade_to_target = mean(saccade_to_target, na.rm = T),
            saccade_to_singleton = mean(saccade_to_singleton, na.rm = T),
            saccade_to_nonsingleton = mean(saccade_to_nonsingleton, na.rm = T)/mean(num_nonsingletons, na.rm = T),
            num_nonsingletons = mean(num_nonsingletons, na.rm = T))

@@

```{r First Saccade Direction - Plot, echo = FALSE}
saccadePlot_singleton <- saccadeData_means_bycondition %>%
  filter(condition == "Singleton Search", dType != "Absent") %>%
  ggplot(aes(group = dType, y = proportionSaccades, fill = dType, x = stimType, shape = dType, colour = dType)) +
  geom_line(aes(linetype = dType, colour = dType), na.rm = T, size = .5, position = position_dodge(width = .6)) +
  geom_point(aes(group = dType, y = proportionSaccades, x = stimType), na.rm = T, size = 1.5, alpha = .3, stroke = F, data = filter(saccadePlotDataParticipants, condition == "Singleton Search", dType != "Absent"), position = position_jitterdodge(dodge.width = .6, jitter.width = .2)) +
  geom_errorbar(aes(ymin = proportionSaccades-se, ymax = proportionSaccades+se), na.rm = T, linetype = "solid", position = position_dodge(width = .6, preserve = "total"), show.legend = FALSE, colour = "black", width = .3) +
  geom_point(na.rm = T, size = 3, position = position_dodge(width = .6), colour = "black") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) +
  scale_linetype_manual(name = "Trial Type", values = c("solid", "longdash", "dotdash"), guide = guide_legend(), labels = c("High-reward", "Low-reward")) +
  scale_fill_manual(name = "Trial Type", values = vmacCols, labels = c("High-reward", "Low-reward")) +
  scale_colour_manual(name = "Trial Type", values = vmacCols, labels = c("High-reward", "Low-reward")) +
  scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22,23), labels = c("High-reward", "Low-reward")) +
  ylab("% First Saccades") + xlab("Stimulus Type") + labs(tag = "A", title = "Singleton Search") +
  my_theme

@@

```{r First Saccade Direction - Capture ANOVA}
capture.ANOVA <- aov_car(Capture ~ condition*dType + Error(sub/dType), data = captureData_means_byparticipant,  anova_table = list(es="pes"))

capture.ANOVA

@@

1/capture_bayes

@@

```{r First Saccade Direction - Planned t-tests}
Singleton_high.ttest <- captureData_means_byparticipant %>%
  ungroup() %>%
  filter(condition == "Singleton Search") %>%
  filter(dType == "High") %>%
  select(Capture) %>%
  pull() %>%
  t.test()

@@

@@

@@

@@

@@

@@

@@

Feature_low.es <- captureData_means_byparticipant %>%
  ungroup() %>%
  filter(condition == "Feature Search") %>%
  filter(dType == "Low") %>%
  select(Capture) %>%
  summarise(mean_capture = mean(Capture), sd_capture = sd(Capture), d_z = abs(mean_capture/sd_capture)) %>%
  pull(d_z)
```

@@

```{r Block Analysis Graph}
capturePlot_byblock_singleton <- 
  capturemeans_byblock %>%
  filter(condition == "Singleton Search") %>%
  ggplot(aes(x = newblock, y = capture, group = dType, shape = dType, colour = dType)) +
  #geom_rect(fill = "#D3D3D3", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = 0, alpha = .3, inherit.aes = F) +
  geom_hline(yintercept = 0, colour = "black", size = .5, linetype = "dotted") +
  annotate(geom = "text", label = "Capture", x = 4.7, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
  annotate(geom = "text", label = "Suppression", x = 4.7, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
  annotate(geom = "segment", x = 4.5, xend = 4.5, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
  annotate(geom = "segment", x = 4.5, xend = 4.5, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
  geom_line(aes(linetype = dType), size = .5) +
  geom_errorbar(aes(ymin = capture - se, ymax = capture + se), width = .1, colour = "black") +
  geom_point(aes(shape = dType, fill = dType), size = 3, colour = "black") +
  scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22)) +
  scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) +
  scale_colour_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) +
  scale_y_continuous(expand = c(0,0), limits = c(-.3,.301), breaks = seq(-.3, .3, .1), labels = scales::percent_format(accuracy = 1)) +
  scale_x_discrete() +
  coord_cartesian(xlim = c(1,4),
                  clip = 'off') +
  scale_linetype_manual(name = "Distractor Type", values = c("solid", "longdash"), guide = guide_legend()) +
  ylab("Capture Score") + xlab("Epoch (96 trials)") + labs(tag = "A", title = 'Singleton Search') +
  my_theme

@@

capture_byblock.ANOVA

@@

capture_byblock.polys
```

>>>>

---
title: "Analysis Report"
author: "Daniel Pearson"
date: "11 April 2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(R.matlab)
library(afex)
library(emmeans)
library(here)
library(patchwork)
library(cowplot)
library(BayesFactor)
library(hrbrthemes)
library(ggsignif)
library(summarytools)

st_options(bootstrap.css     = FALSE,       # Already part of the theme so no need for it
           plain.ascii       = FALSE,       # One of the essential settings
           style             = "rmarkdown", # Idem.
           dfSummary.silent  = TRUE,        # Suppresses messages about temporary files
           footnote          = NA,          # Keeping the results minimalistic
           subtitle.emphasis = FALSE)       # For the vignette theme, this gives
                                            # much better results. Your mileage may vary.

st_css()

library(knitr)
opts_chunk$set(comment=NA, prompt=FALSE, cache=FALSE, echo=TRUE, results='asis')

source(here::here("R", "dz_calculator.r"))
source(here::here("R", "vmac_pal.R"))
source(here::here("R", "summarySEwithin2.r"))

@@

# Omission Trial Analysis

@@

We first removed participants who had poor gaze data (mean proportion of valid gaze samples during the fixation or trial period < .5).
```{r Remove participants with poor gaze data}
propCutoff <- .5
allTracks <- exptdata %>%
  group_by(sub) %>%
  summarise(fixationProp = mean(fixationPropGoodSamples),
            trialProp = mean(trialPropGoodSamples))

@@

`r length(poortracks)` participants were removed due to having a poor quality eye gaze data.

@@

#  check to make sure that everyone has completed the full 480 trials (e.g., if the experiment crashed/was abandoned due to poor gaze data)
didNotComplete <- exptdata %>%
  group_by(sub) %>%
  filter(block > 0) %>%
  tally() %>%
  filter(n < 480) %>%
  select(sub)

@@

During a post-experiment debrief, participant #37 reported that they thought that they needed to look at the coloured circle in order to earn rewards, and so they were removed from the data set.

Then we removed the first two trials of the experiment, the first two trials after breaks, and timeouts from the data (in line with previous VMAC analysis protocols, e.g. Le Pelley et al, 2015 - __JEP:General__).

@@

This is the data set that we are left with:

```{r Glimpse exptdata after exclusions}
print(dfSummary(exptdata, style = "grid", graph.magnif = 0.75, tmp.img.dir = "/tmp"),  max.tbl.height = 300, method = "render")
```

Key for each of the variables in the table:

```{r table2, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
| Variable name | Explanation                                  |
|---------------|--------------------------------------------|
| block         | Experiment block (1--8; 60 trials per block) |
| trial         | Experiment trial (1--480)      |
| trialCounter  | Trial counter within a block (1--60)      |
| trials_since_break         | Trial counter since last break (same as trialCounter for this experiment) |
| targetLoc         | Location of the target stimulus of 4 possible locations     |
| targetType  | Whether the target was a diamond or a circle (1 - diamond, 2 - circle)    |
| distractLoc         | Location of the singleton distractor (or random non-singleton on distractor absent trials) |
| distractShape         | The shape that defined the singleton distractor (1 - diamond, 2 - circle, 3 - hexagon, 4 - square)      |
| distractType  | Whether it was a high (1), low (2), or absent (3) trial     |
| fixationTime         | Length of fixation period in seconds |
| fixationPropGoodSamples         | The proportion of valid samples within the fixation period     |
| fixationTimeout  | Whether the fixation timeout period (4 seconds) was reached before a valid fixation was recorded  |
| trialPropGoodSamples         | The proportion of valid samples within the trial period |
| timeout         | Whether a hard-timeout (2 seconds) was reached before the target was fixated      |
| softTimeoutTrial  | Whether a soft-timeout (1 second) was reached, meaning that no reward was awarded   |
| omissionTrial         | Whether an omission trial was recorded  |
| rt         | Response time in seconds     |
| trialPay  | The reward for the current trial (in points)    |
| sessionPay         | Total reward accumulated during the experiment (in points) |
| timeOnLoc 1--5         | Amount of time (in seconds) that gaze was recorded on each stimulus location (1--4), and anywhere else (5)     |
| sub  | Participant identifier     |
| counterbal         | Code assigning participants to each condition (singleton vs feature) and colour--reward mapping |
| age         | Age in years     |
| gender  | Self-reported gender (m/f/o)  |
| condition         | Search condition (1 - feature search, 2 - singleton search)    |
| dType  | Distractor type (1 - high, 2 - low, 3 - absent)  |
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

## Omission Trials
```{r Omission Trial Means, message=FALSE, warning=FALSE}
# Calculate mean proportion of omission trials for each trial type, by participant
exptdata_means_byparticipant <- exptdata %>%
  ungroup() %>%
  group_by(sub, condition, dType) %>%
  summarise(m = mean(omissionTrial))

# Calculate mean proportion of omission trials for each trial type, by condition
exptdata_means_bycondition <- summarySEwithin2(data = exptdata_means_byparticipant, measurevar = "m", betweenvars = "condition", withinvars = "dType", idvar = "sub") %>%
  select(-ends_with("Normed"))
```

Draw a graph of omission trials for each condition:

```{r Omission Trial Graph, fig.height=10, fig.width=5.5, message=FALSE, warning=FALSE, echo=FALSE}
omissionPlot_singleton <- exptdata %>%
  filter(condition == "Singleton Search") %>%
  group_by(sub, dType) %>%
  summarise(m = mean(omissionTrial)) %>%
  ggplot(aes(x = dType, y = m, fill = dType, shape = dType)) +
  geom_errorbar(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m, ymin = m-se, ymax = m+se), colour = "black", width = .15) +
  geom_line(aes(group = sub), colour = "black", alpha = .1, linetype = "solid", size = .5) +
  geom_line(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m, group = 1), colour = "black") + 
  geom_point(data = filter(exptdata_means_bycondition, condition == "Singleton Search"), aes(x = dType, y = m), colour = "black", size = 3) +
  geom_signif(comparisons = list(c("High", "Low"), c("Low", "Absent")), annotations = c("***","*"), y_position = c(.61,.57), colour = "black", tip_length = 0) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) +
  scale_x_discrete(labels = c("High\nreward", "Low\nreward", "Distractor\nabsent")) +
  scale_fill_manual(values = vmacCols) +
  scale_colour_manual(values = vmacCols) +
  scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22,23)) +
  labs(y = "% Reward Omissions", x = "Trial Type", tag = "A", title = "Singleton Search") +
  my_theme

@@

### Effect of Reward
Effect of reward ANOVA:
```{r Effect of Reward - Omissions}
omissions_vmac.ANOVA <- aov_car(m ~ condition*dType + Error(sub/dType), data = filter(exptdata_means_byparticipant, dType != "Absent"), anova_table = list(es="pes"))

knitr::kable(nice(omissions_vmac.ANOVA))
```

Planned t-tests:
```{r Effect of Reward - Omissions - Planned t-tests, results="markup"}
singleton_high_omissions <- exptdata_means_byparticipant %>%
  ungroup() %>%
  filter(condition == "Singleton Search") %>%
  filter(dType == "High") %>%
  select(m) %>%
  pull()

@@

singleton_VMAC_omissions.ttest <- t.test(singleton_high_omissions, singleton_low_omissions, paired = T)
singleton_VMAC_omissions.ttest
singleton_VMAC_omissions.es <- dz_calculator(singleton_high_omissions, singleton_low_omissions)
singleton_VMAC_omissions.es
feature_VMAC_omissions.ttest <- t.test(feature_high_omissions, feature_low_omissions, paired = T)
feature_VMAC_omissions.ttest
feature_VMAC_omissions.es <- dz_calculator(feature_high_omissions, feature_low_omissions)
feature_VMAC_omissions.es

@@

vmac_condition_bayes <- ttestBF(x = vmac_singleton, y = vmac_feature)
vmac_condition_bayes
```

@@

knitr::kable(nice(omissions_salience.ANOVA))
```

Planned t-tests:
```{r Effect of Physical Salience - Omissions - Planned t-tests, results="markup"}
singleton_physicalsalience_omissions.ttest <- t.test(singleton_low_omissions, singleton_absent_omissions, paired = T)
singleton_physicalsalience_omissions.ttest
singleton_physicalsalience_omissions.es <- dz_calculator(singleton_low_omissions, singleton_absent_omissions)
singleton_physicalsalience_omissions.es

feature_physicalsalience_omissions.ttest <- t.test(feature_absent_omissions, feature_low_omissions, paired = T) # reverse the order here so can get positive t value
feature_physicalsalience_omissions.ttest
feature_physicalsalience_omissions.es <- dz_calculator(feature_low_omissions, feature_absent_omissions)
feature_physicalsalience_omissions.es
```

@@

```{r Glimpse saccadedata}
print(dfSummary(saccadedata, style = "grid", graph.magnif = 0.75, tmp.img.dir = "/tmp"),  max.tbl.height = 300, method = "render")
```

Key for each of the new variables in saccadedata data frame:

```{r table3, echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl2 <- "
| Variable name | Explanation                                  |
|---------------|--------------------------------------------|
| latency         | Saccade latency in milliseconds |
| loc 1--5         | Whether the first saccade was directed towards location 1--4, or somewhere else (loc 5)      |
| discardTrial  | Whether the trial should be excluded from saccade analyses due to exclusion criteria      |
| anticipatorySaccade         | Whether saccade latency was <80ms |
| outsideFixation         | Trials in which no gaze was reocrded within 100 pixels of fixation in the first 80 ms    |
| noSaccades  | Trials in which the saccade identification algorithm did not detect a saccade   |
| noValidData         | Trials in which there was insufficient valid gaze data to detect a saccade |
| first_saccade_loc         | The direction of the first saccade (locations 1--4, or elsewhere [loc 5])     |
| saccade_to_target  | Whether the first saccade was directed towards the target    |
| saccade_to_nonsingleton         | Whether the first saccade was directed towards one of the non-singleton distractors |
| num_nonsingletons         | The number of non-singleton distractors in the display (2 on high and low trials, 3 on distractor absent trials)     |
"
cat(tabl2) # output the table in a format good for HTML/PDF/docx conversion
```

## First saccade direction
```{r First saccade direction - means, warning=FALSE, message=FALSE}
# calculate summary statistics for each participant
saccadeData_means_byparticipant <- saccadedata %>%
  ungroup() %>%
  mutate(sub = as.factor(sub)) %>%
  group_by(sub, condition, dType) %>%
  summarise(saccade_to_target = mean(saccade_to_target, na.rm = T),
            saccade_to_singleton = mean(saccade_to_singleton, na.rm = T),
            saccade_to_nonsingleton = mean(saccade_to_nonsingleton, na.rm = T)/mean(num_nonsingletons, na.rm = T),
            num_nonsingletons = mean(num_nonsingletons, na.rm = T))

@@

Graph of the first saccade data and capture scores:

```{r First Saccade Direction - Plot, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}
saccadePlot_singleton <- saccadeData_means_bycondition %>%
  filter(condition == "Singleton Search", dType != "Absent") %>%
  ggplot(aes(group = dType, y = proportionSaccades, fill = dType, x = stimType, shape = dType, colour = dType)) +
  geom_line(aes(linetype = dType, colour = dType), na.rm = T, size = .5, position = position_dodge(width = .6)) +
  geom_point(aes(group = dType, y = proportionSaccades, x = stimType), na.rm = T, size = 1.5, alpha = .3, stroke = F, data = filter(saccadePlotDataParticipants, condition == "Singleton Search", dType != "Absent"), position = position_jitterdodge(dodge.width = .6, jitter.width = .2)) +
  geom_errorbar(aes(ymin = proportionSaccades-se, ymax = proportionSaccades+se), na.rm = T, linetype = "solid", position = position_dodge(width = .6, preserve = "total"), show.legend = FALSE, colour = "black", width = .3) +
  geom_point(na.rm = T, size = 3, position = position_dodge(width = .6), colour = "black") +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(0,.8)) +
  scale_linetype_manual(name = "Trial Type", values = c("solid", "longdash", "dotdash"), guide = guide_legend(), labels = c("High-reward", "Low-reward")) +
  scale_fill_manual(name = "Trial Type", values = vmacCols, labels = c("High-reward", "Low-reward")) +
  scale_colour_manual(name = "Trial Type", values = vmacCols, labels = c("High-reward", "Low-reward")) +
  scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22,23), labels = c("High-reward", "Low-reward")) +
  ylab("% First Saccades") + xlab("Stimulus Type") + labs(tag = "A", title = "Singleton Search") +
  my_theme

@@

```{r First Saccade Direction - Capture ANOVA, results="markup", message = FALSE}
capture.ANOVA <- aov_car(Capture ~ condition*dType + Error(sub/dType), data = captureData_means_byparticipant,  anova_table = list(es="pes"))

knitr::kable(nice(capture.ANOVA))

@@

capture_bayes

@@

```{r First Saccade Direction - Planned t-tests, results = "markup"}
Singleton_high.ttest <- captureData_means_byparticipant %>%
  ungroup() %>%
  filter(condition == "Singleton Search") %>%
  filter(dType == "High") %>%
  select(Capture) %>%
  pull() %>%
  t.test()

Singleton_high.ttest

@@

Singleton_high.es

@@

Singleton_low.ttest

@@

Singleton_low.es

@@

Feature_high.ttest

@@

Feature_high.es

@@

Feature_low.ttest

@@

Feature_low.es <- captureData_means_byparticipant %>%
  ungroup() %>%
  filter(condition == "Feature Search") %>%
  filter(dType == "Low") %>%
  select(Capture) %>%
  summarise(mean_capture = mean(Capture), sd_capture = sd(Capture), d_z = abs(mean_capture/sd_capture)) %>%
  pull(d_z)

Feature_low.es
```

@@

```{r Block Analysis Graph, echo=FALSE, fig.height=10, fig.width=5, message=FALSE, warning=FALSE}
capturePlot_byblock_singleton <- 
  capturemeans_byblock %>%
  filter(condition == "Singleton Search") %>%
  ggplot(aes(x = newblock, y = capture, group = dType, shape = dType, colour = dType)) +
  #geom_rect(fill = "#D3D3D3", xmin = -Inf, xmax = Inf, ymin = -Inf, ymax = 0, alpha = .3, inherit.aes = F) +
  geom_hline(yintercept = 0, colour = "black", size = .5, linetype = "dotted") +
  annotate(geom = "text", label = "Capture", x = 4.7, y = .15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
  annotate(geom = "text", label = "Suppression", x = 4.7, y = -.15, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
  annotate(geom = "segment", x = 4.5, xend = 4.5, y = -.03, yend = -.27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
  annotate(geom = "segment", x = 4.5, xend = 4.5, y = .03, yend = .27, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
  geom_line(aes(linetype = dType), size = .5) +
  geom_errorbar(aes(ymin = capture - se, ymax = capture + se), width = .1, colour = "black") +
  geom_point(aes(shape = dType, fill = dType), size = 3, colour = "black") +
  scale_shape_manual(name = "Distractor Type", guide = guide_legend(), values = c(21,22)) +
  scale_fill_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) +
  scale_colour_manual(name = "Distractor Type", values = vmacCols, guide = guide_legend()) +
  scale_y_continuous(expand = c(0,0), limits = c(-.3,.301), breaks = seq(-.3, .3, .1), labels = scales::percent_format(accuracy = 1)) +
  scale_x_discrete() +
  coord_cartesian(xlim = c(1,4),
                  clip = 'off') +
  scale_linetype_manual(name = "Distractor Type", values = c("solid", "longdash"), guide = guide_legend()) +
  ylab("Capture Score") + xlab("Epoch (96 trials)") + labs(tag = "A", title = 'Singleton Search') +
  my_theme

@@

knitr::kable(nice(capture_byblock.ANOVA))

@@

knitr::kable(capture_byblock.polys)
```

## Vincentized Analysis

This analysis looks at the percentage of trials captured/suppressed by each distractor as a function of saccade latency.

```{r Vincentized Analysis - Data Tidying}
quartiles_cutoffs <- saccadedata %>%
  group_by(sub, dType, condition) %>%
  summarise(q1 = quantile(latency, probs = .25, na.rm = T), q2 = quantile(latency, probs = .5, na.rm = T), q3 = quantile(latency, probs = .75, na.rm = T), q4 = quantile(latency, probs = 1, na.rm = T))

quartiles_cutoffs_figures <- saccadedata %>% 
  group_by(sub, dType, condition) %>%
  summarise(qs = list(enframe(quantile(latency, probs=seq(.25,.75,.25), na.rm = T)))) %>% 
  unnest

saccadedata <- full_join(saccadedata, quartiles_cutoffs, by = c("sub","dType", "condition"))

saccadedata <- saccadedata %>% 
  mutate(quartile = case_when(latency <= q1 ~ 1,
                              latency <= q2 ~ 2,
                              latency <= q3 ~ 3,
                              latency <= q4 ~ 4))

saccade_latency_quartiles_means_byparticipant <- saccadedata %>%
  ungroup() %>%
  drop_na(quartile) %>% 
  group_by(sub, condition, dType, quartile) %>%
  summarise(mean_latency = mean(latency, na.rm = T))

saccade_latency_quartiles_means_bycondition <- summarySEwithin2(saccade_latency_quartiles_means_byparticipant, measurevar = "mean_latency", betweenvars = "condition", withinvars = c("dType", "quartile"), idvar = "sub") %>%
  select(-ends_with("Normed"))

saccade_direction_quartiles_means_byparticipant <- saccadedata %>%
  ungroup() %>%
  drop_na(quartile) %>% 
  group_by(sub, condition, dType, quartile) %>%
  summarise(saccade_to_target = mean(saccade_to_target, na.rm = T),
            saccade_to_singleton = mean(saccade_to_singleton, na.rm = T),
            saccade_to_nonsingleton = mean(saccade_to_nonsingleton, na.rm = T)/mean(num_nonsingletons, na.rm = T),
            num_nonsingletons = mean(num_nonsingletons, na.rm = T),
            capture = saccade_to_singleton - saccade_to_nonsingleton) %>%
  filter(dType != "Absent")

saccade_direction_quartiles_means_bycondition <- summarySEwithin2(saccade_direction_quartiles_means_byparticipant, measurevar = "capture", betweenvars = "condition", withinvars = c("dType", "quartile"), idvar = "sub") %>%
  select(-ends_with("Normed")) %>%
  left_join(., saccade_latency_quartiles_means_bycondition, by = c("dType", "condition", "quartile"), suffix = c(".prop", ".latency"))
```

```{r Vincentized Analysis - Graph, echo=FALSE, warning=FALSE, fig.height=10, fig.width=5, message=FALSE}

vincentized_annotations <- c("***"," "," "," ","**"," "," "," ","***"," "," "," ","***"," "," ","")

vincentizedPlot_singleton <- saccade_direction_quartiles_means_bycondition %>%
  mutate(annotations = vincentized_annotations) %>%
  filter(condition == "Singleton Search") %>%
  ggplot(aes(x = mean_latency, y = capture, fill = dType, linetype = dType, colour = dType)) +
  annotate(geom = "text", label = "Capture", x = 370, y = .3, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
  annotate(geom = "text", label = "Suppression", x = 370, y = -.2, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
  annotate(geom = "segment", x = 365, xend = 365, y = -.03, yend = -.37, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
  annotate(geom = "segment", x = 365, xend = 365, y = .03, yend = .57, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
  geom_linerange(aes(ymin = capture-se.prop, ymax = capture + se.prop), colour = "black", linetype = "solid", size = .5) +
  geom_errorbarh(aes(xmin = mean_latency-se.latency, xmax = mean_latency+se.latency, height = 0), linetype = "solid", size = .5, colour = "black") +
  geom_line(size = .5) +
  geom_point(aes(shape = dType, fill = dType), size = 3, colour = "black") +
  geom_hline(yintercept = 0, colour = "black", size = .5, linetype = "dotted") +
  geom_text(aes(label = annotations), nudge_y = .07, colour = "black") +
  scale_fill_manual(name = "Trial Type", values = vmacCols, guide = guide_legend(), labels = c("High-reward", "Low-reward")) +
  scale_colour_manual(name = "Trial Type", values = vmacCols, guide = guide_legend(), labels = c("High-reward", "Low-reward")) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(-.4,.621)) +
  scale_x_continuous(expand = c(0,0), limits = c(165, 380), breaks = seq(125,375,50)) +
  scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22), labels = c("High-reward", "Low-reward")) +
  scale_linetype_manual(name = "Trial Type", values = c("solid", "longdash"), guide = guide_legend(), labels = c("High-reward", "Low-reward")) +
  coord_cartesian(xlim = c(165,360),
                  clip = 'off') +
  ylab("Capture Score") + xlab("Saccade latency (ms)") + labs(tag = "A", title = 'Singleton Search') +
  my_theme + theme(axis.ticks.x = element_line(colour = "black", size = .5))

vincentizedPlot_feature <- 
  saccade_direction_quartiles_means_bycondition %>%
  mutate(annotations = vincentized_annotations) %>%
  filter(condition == "Feature Search") %>%
  mutate(nudge_y = c(rep(.07, 7), -.07), nudge_x = c(0,0,0,-5,0,0,0,5)) %>%
  ggplot(aes(x = mean_latency, y = capture, fill = dType, linetype = dType, colour = dType)) +
  annotate(geom = "text", label = "Capture", x = 370, y = .3, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
  annotate(geom = "text", label = "Suppression", x = 370, y = -.2, angle = 90, vjust = 1, hjust = .5, family = font_rc) +
  annotate(geom = "segment", x = 365, xend = 365, y = -.03, yend = -.37, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
  annotate(geom = "segment", x = 365, xend = 365, y = .03, yend = .57, arrow = arrow(type = 'closed', length = unit(6, 'pt'))) +
  geom_linerange(aes(ymin = capture-se.prop, ymax = capture + se.prop), colour = "black", linetype = "solid", size = .5) +
  geom_errorbarh(aes(xmin = mean_latency-se.latency, xmax = mean_latency+se.latency, height = 0), linetype = "solid", size = .5, colour = "black") +
  geom_line(size = .5) +
  geom_point(aes(shape = dType, fill = dType), size = 3, colour = "black") +
  geom_hline(yintercept = 0, colour = "black", size = .5, linetype = "dotted") +
  geom_text(aes(label = annotations, y = capture + nudge_y, x = mean_latency), colour = "black") +
  scale_fill_manual(name = "Trial Type", values = vmacCols, guide = guide_legend()) +
  scale_colour_manual(name = "Trial Type", values = vmacCols, guide = guide_legend()) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1), expand = c(0,0), limits = c(-.4,.621)) +
  scale_x_continuous(expand = c(0,0), limits = c(165, 380), breaks = seq(125,375,50)) +
  scale_linetype_manual(name = "Trial Type", values = c("solid", "longdash"), guide = guide_legend()) +
  scale_shape_manual(name = "Trial Type", guide = guide_legend(), values = c(21,22)) +
  coord_cartesian(xlim = c(165,360),
                  clip = 'off') +
  ylab("Capture Score") + xlab("Saccade latency (ms)") + labs(tag = "B", title = 'Feature Search') +
  my_theme + theme(axis.ticks.x = element_line(colour = "black", size = .5))
